### 2025-02-26 manuscript/manuscript.tex
add ref
update authors

\begin{center}
    {\Huge Island-Wide Soil integration: the case of Crete}\\[2em]
    {\large Savvas Paragkamian, Panagiotis F. Sarris, Evangelos Pafilis, Georgios Kotoulas}\\[1em]
    {\large \today}
\end{center}

@@

>>>>

\begin{center}
    {\Huge Island-Wide Soil integration: the case of Crete}\\[2em]
    {\large Savvas Paragkamian, Neil Davies, Panagiotis F. Sarris, Evangelos Pafilis, Georgios Kotoulas}\\[1em]
    {\large \today}
\end{center}

@@

towards a soil biodiversity platform \parencite{ramirez2015toward}
